World Heritage Sites on Wikipedia: Cultural Heritage Activism in a Context of Constrained Agency

### 2021-03-31 analysis/paper/paper.Rmd
tamp

The most striking spatial pattern in our results is the high proportion of anonymous edits (as the only type of edit that can be geolocated) that come from the United States on articles about CS-WHL sites, regardless of where in the world the CS-WHL site is located. These anonymous editors of articles about CS-WHL are generally not located in the same country as the site they are editing. Finding the United States at the first ranked location for anonymous edits is not surprising as it has the world's largest number of English speakers. We might similarly expect that the French language Wikipedia (2.3 m articles, 173 m edits, 3.9 m users) would have more edits originating in France or francophone on articles about CS-WHL sites in any part of the world. We have limited the scope of our initial foray into this topic to the English language Wikipedia because it is the largest by a considerable margin [6.2 m articles, 998 m edits, 40 m users, @wiki:listoflangs]. The question of whether or not our findings generalise to non-English-language Wikipedias should be priority for future research.

@@

The agency of people participating in heritage-related activities on Wikipedia is highly constrained by the technical characteristics of editing, bots, and consensus-valuing culture. Although there are some niches where editors can debate, concerns about state-like actors, violence & destruction, deal-making, etc. are minor. Typical conflicts about Wikipedia CS-WHL articles are hyper-local, and process-centered. There are also cases of editorial conflicts about substantive issues of specific CS-WHL, such as Mapungubwe and Preah Vihear, that include editors with a personal investment in the debate, if not the article. Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the Anglosphere, and poor coverage of CS-WHL in the Global South. Because of these technical and cultural characteristics of Wikipedia, its articles present a discourse that actively obscures the power relations that give rise to them, and makes opaque debates about how heritage is involved in the production of identity and power [cf. @harvey2001heritage].

>>>>

The most striking spatial pattern in our results is the high proportion of anonymous edits (as the only type of edit that can be geolocated) that come from the United States on articles about CS-WHL sites, regardless of where in the world the CS-WHL site is located. These anonymous editors of articles about CS-WHL are generally not located in the same country as the site they are editing. Finding the United States at the first ranked location for anonymous edits is not surprising as it has the world's largest number of English speakers. We might similarly expect that the French language Wikipedia (2.3 m articles, 173 m edits, 3.9 m users) would have more edits originating in France or francophone on articles about CS-WHL sites in any part of the world. We have limited the scope of our initial foray into this topic to the English language Wikipedia because it is the largest by a considerable margin [6.2 m articles, 998 m edits, 40 m users, @wiki:listoflangs]. The narrow linguistic focus of our study is an important limitation, and question of whether or not our findings generalise to non-English-language Wikipedias should be priority for future research.

@@

The agency of people participating in heritage-related activities on Wikipedia is highly constrained by the technical characteristics of editing, bots, and consensus-valuing culture. Although there are some niches where editors can debate, concerns about state-like actors, violence & destruction, deal-making, etc. are minor. Typical conflicts about English-language Wikipedia CS-WHL articles are hyper-local, and process-centered. There are also cases of editorial conflicts about substantive issues of specific CS-WHL, such as Mapungubwe and Preah Vihear, that include editors with a personal investment in the debate, if not the article. Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the Anglosphere, and poor coverage of CS-WHL in the Global South. Because of these technical and cultural characteristics of Wikipedia, its articles present a discourse that actively obscures the power relations that give rise to them, and makes opaque debates about how heritage is involved in the production of identity and power [cf. @harvey2001heritage].
